Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-21 paper/Draft.tex
First set of histograms of revisions in meanforecast and uncertainty

Another prediction from FIRE is that there is unambigous uncertainty reduction as one appraoches to the date of realization. Figure \ref{RevisionHist} plots the average revision in forecasts and uncertainty. The the more negative the revision lies in, the more rational of the forecast.

@@

\begin{figure}[h]\label{RevisionHist}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMeanRev_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVarRev_hist.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/PRCPCEMeanRev_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVarRev_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/SCEMeanRev_hist.png} 
	\includegraphics[width=6cm]{figures/SCEVarRev_hist.png}  \\
	\caption{Distribution of Revision in Uncertainty}
\end{figure}

>>>>

Another prediction from FIRE is that there is unambigous uncertainty reduction as one appraoches to the date of realization. Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty. The the more negative the revision lies in, the more rational of the forecast.

@@

\begin{figure}[h]\label{RevisionHist}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMean_rv_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVar_rv_hist.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/PRCPCEMean_rv_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVar_rv_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/SCEMean_rv_hist.png} 
	\includegraphics[width=6cm]{figures/SCEVar_rv_hist.png}  \\
	\caption{Distribution of Revision in Forecasts}
\end{figure}
